gij bent 2

### 2025-08-21 paper/paper.qmd
paragraph introducing terms innovators and early adopters

Within the propagation of linguistic change, different roles can be distinguished. Innovators, who are hypothesized to be less central and only loosely connected to others through weak ties, acquiring novel linguistic features from outside their immediate community [@rogers_diffusion_2003: 282-283]. Early adopters, by contrast, are hypothesized to be more centrally positioned and to enjoy a higher degree of connectivity within the population. Through their many strong ties, they amplify and legitimize the innovation, spreading it efficiently across their dense local networks [@rogers_diffusion_2003: 282-283]. In this way, innovators and early adopters together bridge the gap between the periphery and the core of a community, ensuring that new linguistic forms do not remain isolated but instead gain broader social traction [@granovetter_strength_1973;@milroy_linguistic_1985]. The idea that innovation originates in the periphery of a network before it can spread has been attested before in network studies [@van_de_leemput_transformation_2024], but not whithin linguistics.

>>>>

Within the propagation of linguistic change, different roles can be distinguished. Innovators, who are hypothesized to be less central and only loosely connected to others through weak ties, acquiring novel ideas from outside their immediate community [@rogers_diffusion_2003: 282-283]. Early adopters, by contrast, are hypothesized to be more centrally positioned and to enjoy a higher degree of connectivity within the population. Through their many strong ties, they amplify and legitimize the innovation, spreading it efficiently across their dense local networks [@rogers_diffusion_2003: 282-283]. In this way, innovators and early adopters together bridge the gap between the periphery and the core of a community, ensuring that new linguistic forms do not remain isolated but instead gain broader social traction [@granovetter_strength_1973;@milroy_linguistic_1985]. The idea that innovation originates in the periphery of a network before it can spread has been attested before in network studies [@van_de_leemput_transformation_2024], but not whithin linguistics.
